---
title: "Leaf-level coordination principles propagate to the ecosystem scale"
author: "Ulisse Gomarasca et al."
date: "2023-03-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Description

This R Markdown document guides you through the code used for the analysis in the
manuscript titled: Leaf-level coordination principles propagate to the ecosystem scale".

For the analysis, we used R 4.1.0, and RStudio 2022.12.0 Build 353.
The main packages used are described in the Methods section of the manuscript.




## Manuscript analysis and figures

Here, we run the code used to generate the principal component analysis output
and plots for Figures 1, 2, and 3.
Supplementary Table 7 is also 

```{r}
rm(list = ls(all = TRUE)) # clear environment

source("scripts/PCAs.R") # function to run the analyses

print("Running PCA analysis to reproduce results of the manuscript titled: 'Leaf-level coordination principles propagate to the ecosystem scale'. This can take a few hours.")

savedata <- as.logical(readline(prompt = "Save the output of the PCA for Figures 1, 2, 3? T/F:")) # ask if output should be saved

PCAs(figs = 1:3) # 1 for Figure 1; 2 for Figure 2; 3 for Figure 3
```


## Supplementary Figures 1, 3, 8

Here, we run the principal component analysis again with i) all sites, ii) forest
sites, and iii) evergreen needle-leaf forest sites, and plot the output into
Supplementary Figures 1, 3, and 8.

```{r}
rm(list = ls(all = TRUE)) # clear environment

print("Running PCA analysis to reproduce Supplementary Figures 1, 3, and 8 in the Supplementary information for the manuscript titled: 'Leaf-level coordination principles propagate to the ecosystem scale'. This can take a few hours.")

savedata <- as.logical(readline(prompt = "Save the output of the PCA for Supplementary Figures 1, 3, 8? T/F:")) # ask if output should be saved

source("scripts/PCA_SuppFig1-3-8.R")
```


## Supplementary Figures 4, 5, 6, 7

Here, we run the principal component analysis for the Least-Cost Hypothesis at
the ecosystem scale with different variables, and plot the output into
Supplementary Figures 4 to 7.

```{r}
rm(list = ls(all = TRUE)) # clear environment

source("scripts/PCAs.R") # function to run the analyses

print("Running PCA analysis to reproduce Supplementary Figures 4, 5, 6, and 7 in the Supplementary information for the manuscript titled: 'Leaf-level coordination principles propagate to the ecosystem scale'. This can take a few hours.")

savedata <- as.logical(readline(prompt = "Save the output of the PCA for Supplementary Figures 4, 5, 6, 7? T/F:")) # ask if output should be saved

PCAs(figs = 31:34) # 31:34 for Supplementary Figures 4-7; 11:12 for additional analyses related to the leaf economics spectrum at the ecosystem scale (not included)
```


## Supplementary Figure 2

Here, we run a set of predictive analysis that include multimodel inference and
relative importance to plot Supplementary Figure 2.

```{r}
rm(list = ls(all = TRUE)) # clear environment

print("Running multimodel inference and relative importance analysis to reproduce Supplementary Figures 2 in the Supplementary information for the manuscript titled: 'Leaf-level coordination principles propagate to the ecosystem scale'")

savedata <- as.logical(readline(prompt = "Save the output of the PCA for Supplementary Figure 2? T/F:")) # ask if output should be saved

source("scripts/multimodel_inference_SuppFig2.R")
```


## Supplementary Table 5

Here, we run a simple linear mixed model to guide the outlook for modeling
purposes.

```{r}
rm(list = ls(all = TRUE)) # clear environment

savedata <- as.logical(readline(prompt = "Save output for linear mixed models? T/F:")) # ask if output should be saved

source("scripts/linear_mixed_model_revisionNatComm.R")
```